\Title

### 2020-12-10 manuscript/manuscript.tex
Finish the boosting description

The gradient boosting algorithm for finding the damped least-squares solutions
for the $K$ parameters vectors $\mathbf{c}_k$ in
equation~\ref{eq:gb-linear-model} can be modified from \citep{friedman2001}

\begin{algorithm}[!h]
  \DontPrintSemicolon
  \setstretch{1.5}
  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
  \For{ $k = 1$ \KwTo $K$ }{
    $\mathbf{B}_k = \mathbf{A}_k \mathbf{S}_k\inv$ \;
    $
     \hat{\mathbf{m}}_k = \left[\mathbf{B}_k\trans \mathbf{W}_k \mathbf{B}_k +
     \lambda \mathbf{I} \right]\inv \mathbf{B}_k\trans \mathbf{W}_k
     \mathbf{r}_{k-1}
    $ \;
    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$ \;
    $
      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
      \left(
        \left\lVert
          \mathbf{r}_{k - 1} - \alpha \mathbf{A}_k \hat{\mathbf{c}}_k
        \right\rVert ^ 2
      \right)
    $ \;
    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{A}_k \hat{\mathbf{c}}_k$ \;
  }
  \BlankLine
  \setstretch{1}
  \caption{Gradient boosting solution for damped least-squares regression.}
\end{algorithm}

The algorithm above works by fitting each component of the additive model, one
at a time, to the residuals of the previous component.

By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
with the observed data) is used to fit the $\mathbf{c}_k$
coefficients and $\alpha_k$ step-size parameter, and then updated by removing
the effect of the same sources, as follows:

\begin{equation}
    \mathbf{r}_0 = \mathbf{d},
\end{equation}

\begin{equation}
    \mathbf{r}_k = \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k.
    \label{eq:residue}
\end{equation}

\noindent On each iteration the $\mathbf{c}_k$ vector and the $\alpha_k$
parameter can be fitted so they minimize the misfit function:

\begin{equation}
    \phi(\mathbf{c}_k) =
        \left\lVert
            \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
\end{equation}

\noindent following the same method described on Section
\ref{sec:eql-inversion}.
Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
adjusting the size of the overlapping windows can help in reducing the computer
memory needed to fit the source coefficients.
Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
matrices large enough that they cannot be stored in memory, we can apply one
more simplification on the fitting process: ignore the effect of the $k$-th
sources on any observation point that falls outside the $k$-th window.

Assuming that there are $N_k$ observation points that fall under the $k$-th
window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
misfit function:

\begin{equation}
    \phi(\mathbf{c}_k) =
        \left\lVert
            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
\end{equation}

\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
observation points that fall under the $k$-th window; and
$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between these observation points
and the $k$-th sources.
Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
elements, the computer memory needed for fitting the $\mathbf{c}_k$
coefficients is greatly reduced.

Once the $\mathbf{c}_k$ coefficients are fitted following the same method
described on Section \ref{sec:eql-inversion}, we need to obtain the value
of the step-size parameter $\alpha_k$.
This can be achieved by minimizing the norm of the difference between the
previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th sources on
every observation point:

\begin{equation}
    \alpha_k = \underset{\alpha}{\mathrm{argmin}}
    \left(
        \left\lVert
            \mathbf{r}_{k-1} - \alpha \mathbf{A}_k \mathbf{c}_k
        \right\rVert ^ 2
    \right),
\end{equation}

\noindent which leads to:

@@

This step will improve the convergence of the iterative algorithm and also will
introduce at some extent the effect of the $k$-th sources on every data point,
which was neglected on the fitting of the $\mathbf{c}_k$ coefficients.

Once both the $\alpha_k$ parameter and the $\mathbf{c}_k$ coefficients are
fitted, equation \ref{eq:residue} is applied to update the residue: compute the
effect of the sources belonging to the $k$-th window on every observation
point. Worth noting that when calculating the effect of any number of sources
we don't need to pre-compute the entire Jacobian matrix: we can calculate the
effect of the sources on each observation point by a simple addition of terms,
what means computing each Jacobian element at once when needed.

Because the number of windows is fixed before starting the iteration process,
its number of steps are also fixed to $K$. Moreover, the windows are randomly
shuffled before starting the process to prevent the prioritization of clustered
sets of equivalent sources.

After all $\alpha_k$ parameters and $\mathbf{c}_k$ coefficients vectors are
fitted, we can predict the effect of every equivalent source on any point as
follows:

\begin{equation}
    V(\mathbf{p}) =
    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
    \frac{\alpha_k {c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
\end{equation}

>>>>

The gradient boosting algorithm above works by fitting each component of the
additive model, one at a time, to the residuals of the previous component.
\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
optimization in the so-called ``function space'', with $\alpha_k$ corresponding
to step sizes in steepest descent.
We can modify the gradient boosting algorithm of \citet{friedman2001} to
find the damped least-squares solutions for the $K$ parameters vectors
$\mathbf{c}_k$ and step sizes $\alpha_k$ in equation~\ref{eq:gb-linear-model}:

\begin{algorithm}[!h]
  \DontPrintSemicolon
  \setstretch{1.5}
  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
  \For{ $k = 1$ \KwTo $K$ }{

    \nllabel{alg:scale}
    $\mathbf{B}_k = \mathbf{A}_k \mathbf{S}_k\inv$ \;

    \nllabel{alg:fit}
    $
     \hat{\mathbf{m}}_k = \left[\mathbf{B}_k\trans \mathbf{W}_k \mathbf{B}_k +
     \lambda \mathbf{I} \right]\inv \mathbf{B}_k\trans \mathbf{W}_k
     \mathbf{r}_{k-1}
    $ \;

    \nllabel{alg:unscale}
    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$ \;

    \nllabel{alg:stepsize}
    $
      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
      \left(
        \left\lVert
          \mathbf{r}_{k - 1} - \alpha \mathbf{A}_k \hat{\mathbf{c}}_k
        \right\rVert ^ 2
      \right)
    $ \;

    \nllabel{alg:residual}
    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{A}_k \hat{\mathbf{c}}_k$ \;
  }
  \BlankLine
  \setstretch{1}
  \caption{Gradient boosting solution for damped least-squares regression.}
\end{algorithm}

\citet{friedman2002} suggests that introducing randomness into the fitting
process can improve convergence of the solution. To achieve this, we randomize
the order in which the $K$ windows are used in the gradient boosting algorithm.

The $\mathbf{A}_k$ matrices have only $N \times M_k$ elements, which can be
considerably smaller than the $N \times M$ elements of $\mathbf{A}$.
Therefore, the gradient boosting method allows us to fit
equivalent sources models that would produce Jacobian matrices that are larger
than the available computer memory.
Furthermore, we can increase or decrease the size of the overlapping windows as
needed depending on the number of sources in the model and the available
computer memory.

We can improve the efficiency of the algorithm further by using only data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:stepsize} and \ref{alg:residual}).
By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
elements.
The forward modeling operations performed in steps \ref{alg:stepsize} and
\ref{alg:residual} can be done by a summation
(TODO: ADD EQUATION)
instead of a matrix-vector product, which allows us to avoid storing the larger
$N \times M_k$ Jacobian.
The influence of distance sources on the solution is maintained by using the
entire set of data points when updating the residuals vector.

The step size parameter functions as scaling factor that prevents the algorithm
from worsening the fit to data points outside of the current window.
As such, it improves the converge of the solution and ensures that the
overall misfit decreases with iteration.
The step size that minimizes the misfit function in step \ref{alg:stepsize} of
the algorithm is

@@

After all $\alpha_k$ step sizes and $\hat{\mathbf{c}}_k$ coefficients vectors
are estimated, we can predict the effect of the additive equivalent source
model on any point through the summation

\begin{equation}
    d(\mathbf{p}) =
    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
    \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
    \ .
\end{equation}

SOMETHING ABOUT THE VON FRESE 88 PAPER (BOOTSTRAP INVERSION) AND HOW THIS IS
DIFFERENT.
